Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-06 draft.tex
add section app analysis

>>>>

\subsection{Application Analysis}
\label{sec:app analysis}

The random job placement and adaptive routing can reach hot-spots free and load-balanced by distributing the workload traffic over the network. In this section, we will show that not every application can benefit from random job placement and adaptive routing.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random job placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}

Figure \ref{fig:apps-commtime} shows the communication time of three applications running concurrently with 4 different placement and routing configurations. MG and CR can get improvement with random placement and adaptive routing, compared with contiguous placement and minimal routing. However, AMG's performance is impacted with random placement and adaptive routing, which makes it an exception from other applications.

The results of random placement shown in Figure \ref{fig:apps-commtime} are collected from extensive runs of different random placements, which can eliminate the possibility of variations.

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-router-traffic}.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:amg-tl-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}%
   \caption{AMG router traffic.}
   \label{fig:amg-router-traffic}
\end{figure*}

Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.
